---
output:
  html_document: default
  pdf_document: default
  word_document: default
---
```{r include = FALSE}
if(!knitr:::is_html_output())
{
  options("width"=56)
  knitr::opts_chunk$set(tidy.opts=list(width.cutoff=56, indent = 2), tidy = TRUE)
  #knitr::opts_chunk$set(fig.pos = 'h',  fig.align="center")
}
```
# Implementation Guide

## Introduction
This guide is a suggestion for implementation and is intended as a starting point for discussion with the understanding that each learning environment may have unique needs and challenges. Below, a suggested schedule is provided to guide in-class delivery. Additionally, a few notes are provided to assist the faciltiator(s) to help create a positive learning experience for all students and instructors alike.  

## Schedule
The following schedule assumes a 5-hour total delivery time with two sessions spanning one lunch/meal period at the midpoint of the delivery.

```{r echo = FALSE}
#implentation 
#hours
time1<-c("09:30","09:35","10:15","10:30","11:30","12:00")
time2<-c("09:30","09:35","10:15","10:30","11:30","12:00")
activity1<-c("Welcome", "Data Exploration",      "Break","Guest Musician", "Instrument Construction",  "Lunch")
activity2<-c("Welcome", "Notation & Composition","Break","Finalize Construction, Notation, and Composition","Performances & Summary","Lunch")
impDF<-data.frame(time1,activity1,activity2)
names(impDF) <- c("Time", "Day 1", "Day 2")

knitr::kable(
  impDF, booktabs = TRUE,
  caption = 'Suggested implementation timeline.'
)
```

## Facilitator Notes
The following notes may help you in your role as a facilitator. 

- You are a facilitator, not an instructor. Guide students to find their own way, their own solutions to problems, and their own learning.

- This should be a creative, fun activity. Make this a priority and learning will follow.

- Students should be engaged in small teams to help each other learn as peer-mentors. Encourage discussion among teams to arrive at solutions. If a team struggles, introduce that team to another group of peers to continue discussions with fresh ideas.

- Students may be challenged with musical aspects of this activity. Look for musically-adept students that may be willing to add their input to discussions around the room. Take advantage of the expertise in the room!

- You may see a wide variety in notation and playing styles. Encourage logic, reproducibility, connections to data, and clarity in justification. As long as students can connect what they play to their data understanding and observations, they have met the challenge presented in this activity. Their musical notation should make sense to not only themselves but to others who may need to play the piece. Ensure the notation systems devised by student teams make sense to others. 

- Ask questions frequently to encourage discussion but also to assess the progress of the student teams. Check in with each team to check their understanding of the timeline so no team gets stuck. 

- Ask teams to pre-design new solutions if they had more free time to do so. What would the next-generation didgeridoo look like if you could build it again? How would you change your design if you had more (time, materials,...)?


